% !TEX program = XeLaTeX
\documentclass[]{friggeri-cv}

\begin{document}
\header{Praveen Kumar }{Pendyala}{In pursuit of building clean, efficient \& accessible tools to help everyone acheive more}

% In the aside, each new line forces a line break
\begin{aside}
    \section{Information}
        \noindent\rule{3cm}{0.5pt}
        %DOB: 26.10.1992
        \href{http://pkp.io}{http://pkp.io}
        \href{https://github.com/praveendath92}{github/praveendath92}
    \section{Contact}
        \href{mailto:praveendath92@gmail.com}{praveendath92@gmail.com}
        (+44) 7763089654
        IG1 2ZJ, London
        United Kingdom
    ~
    \section{Skills}
        \noindent\rule{3cm}{0.5pt}
    \section{Programming}
        Java, Kotlin, Python, C++, TypeScript, Node
    \section{Android}
        Architecture Components, Proguard, Dex, Material design, Life-cycle, CameraX, OpenGL ES, Native code using C++, Benchmark, Profiler
    \section{Build tools}
        Gradle, Maven, Jenkins, Azure DevOps, GitHub Workflows
    \section{Testing}
        Unit testing, Automated UI testing, Smoke testing, AB testing, Experimentation, Performance bechmarking, Memory leak testing
    \section{MOOCs}
        Machine Learning 
        (grade: 97.3\%)
        ~
        Algorithms: Design and Analysis, Part 1 
        (grade: 95.6\%)
\end{aside}
~
\section{Education}
    \begin{entrylist}
        \entry
            {2014–2016}
            {Masters, {\normalfont Distributed Software Systems}}
            {Technische Universität Darmstadt}
            {\emph{GPA of 3.9 out of 4.0 -- converted from 1.55 in German grading.}}
        \entry
            {2010–2014}
            {Bachelors, {\normalfont Electrical Engineering}}
            {Indian Institute of Technology Bombay}
            {}%GPA: 7.49 / 10}
    \end{entrylist}
    \vspace{-0.3cm}

\section{Experience}
    \begin{entrylist}
        \entry
            {2017-now}
            {Microsoft London, SwiftKey Android team}
            {Software Engineer}
            {\emph{Responsible for building and delivering updates of SwiftKey Keyboard to over 500 million users at a biweekly cadence.
    	    \newline 
    	    \newline
    	    Tech lead for delivering Task capture feature. Proposed the use of Android Dynamic Features to run Intelligence models experiments - saving over \$200,000 in server costs to run the experiments in market.
    	    \newline 
    	    \newline
    	    \textbf{Build systems Champion:} Contributed towards multiple build systems and infrastructure migrations and improvements. Re-designed the merge pipeline for a 50\% reduction in run-time.
            \newline
            \newline
            \textbf{Open Source Software Champion:} Responsible for managing compliance in our use of OSS software and our efforts to Open source tools or libraries.
    	    \newline 
    	    \newline
    	    Proposed and implemented a custom file format and 3D rendering engine for Puppets (3D assets in SwiftKey). Files in this format load 45x faster and are 4x smaller than the standard 3D formats. The rendering engine is under 500 KB and capable of rendering over 200+ FPS.
            \newline
            \newline
            Contributed to App size reduction of SwiftKey by investigating optimizations in byte code. Without removing any features we reduced download size by \~50\% (28 MB to 14 MB) and install size by \~40\% (82 MB to 48 MB)}}
    \end{entrylist}

\section{Awards, Publications \& Talks}
	\begin{entrylist}
        \entry
            {Speaker}
            {Effortless, effective navigation with less code}{mDevCamp 2020}
            {}
        \entry
            {Speaker}
            {SwiftKey’s CI / CD using Azure Devops}{Microsoft Android Dev Day 2020}
            {}
        \entry
            {Speaker}
            {Android App size reduction}{Multiple events 2019}
            {\emph{Londroid at Facebook London and DroidCon in Lisbon. Presented our work on how we managed to reduce SwiftKey's download size by 50\%, and install size by 40\%}}
        \entry
            {Award}
            {Received 20,000 euro prize money at CeBIT 2016, Hannover}{}
            {\emph{Winners of MAPPING -- Managing Alternatives for Privacy, Property and Internet Governance, app competition.}}
        \entry
            {Publication}
            {DroidAuditor: Forensic Analysis of Application-Layer Privilege Escalation Attacks on Android}{}
            {\emph{Financial Cryptography and Data Security Conference 2016.}}        
	\end{entrylist}


\end{document}